The human in the loop: volunteer-based metacomputers as a socio-technical system

### 2016-04-24 Alife16/paper.tex
Frequently

\begin{figure}[!htb]
\centering
\includegraphics[width=0.32\linewidth]{time-vs-ips-OS-4-4.png}
\includegraphics[width=0.32\linewidth]{time-vs-ips-OS-4-24.png}
\includegraphics[width=0.32\linewidth]{time-vs-ips-OS-7-31.png}
\includegraphics[width=0.32\linewidth]{time-vs-ips-alife-128.png}
\includegraphics[width=0.32\linewidth]{time-vs-ips-alife-64.png}
\includegraphics[width=0.32\linewidth]{time-vs-ips-alife-32.png}
\caption{Duration of experiments vs. number of different IPs (nodes)
  participating in it, with averages and standard deviation shown as
  red dots; in the case there is a single red dot, there was a single
  experiment in which that many computers participated (for instance, 16
  computers in the experiment in the far left or 29 in the middle
  one). 
Shades of blue indicate how many experiments included that many unique IPs,
so lighter shade for a column of dots indicates that a particular number
of computers happened less frequently, while darker shadow means more frequency. 
From left to right and top to bottom experiments 4/4, 4/24 and 7/31,
followed by experiments with 50 traps, cache=128, 64, 32.}
\label{fig:duration}
\end{figure}
%
We will have to analyze experimental data a bit further to find out why
this happens and also if there are some patterns in the three sets of
experiments. An interesting question to ask, for instance, is if 
by adding more computers it makes the experiment take less time. In fact, as
shown in Figure \ref{fig:duration}, the {\em addition} of more computers does
not seem to contribute to decreasing the time needed to finish the
experiment. However, the cause-effect relationship is not clear at
all. It might be the opposite: since experiments take longer to finish
and might in fact be abandoned with no one contributing for some time,
the probability of someone new joining them is higher. In fact,
with experiments taking a few seconds and due to the way the
experiments are announced, it is quite difficult that several
volunteers join in in such a short period of time, even more if we take
into account that volunteers are not {\em carried over} from previous
experiments. 
%
\begin{figure}[!htb]
\centering
\includegraphics[width=0.95\linewidth]{ips-per-minute-cache=64.png}
\caption{Simultaneous IPs every minute of the experiment with cache =
  64. \label{fig:otisdriftwood}}
\end{figure}

>>>>

\begin{figure}[!htb]
\centering
\includegraphics[width=0.32\linewidth]{time-vs-ips-OS-4-4.png}
\includegraphics[width=0.32\linewidth]{time-vs-ips-OS-4-24.png}
\includegraphics[width=0.32\linewidth]{time-vs-ips-OS-7-31.png}
\includegraphics[width=0.32\linewidth]{time-vs-ips-alife-128.png}
\includegraphics[width=0.32\linewidth]{time-vs-ips-alife-64.png}
\includegraphics[width=0.32\linewidth]{time-vs-ips-alife-32.png}
\caption{Duration of experiments vs. number of different IPs (nodes)
  participating in it, with averages and standard deviation shown as
  red dots; in the case there is a single red dot, there was a single
  experiment in which that many computers participated (for instance, 16
  computers in the experiment in the far left or 29 in the middle
  one). 
Shades of blue indicate how many experiments included that many unique IPs,
so lighter shade for a column of dots indicates that a particular number
of computers happened less frequently, while darker shadow means more. 
From left to right and top to bottom experiments 4/4, 4/24 and 7/31,
followed by experiments with 50 traps, cache=128, 64, 32.}
\label{fig:duration}
\end{figure}
%
We will have to analyze experimental data a bit further to find out why
this happens and also if there are some patterns in the three sets of
experiments. An interesting question to ask, for instance, is if 
by adding more computers it makes the experiment take less time. In fact, as
shown in Figure \ref{fig:duration}, the {\em addition} of more computers does
not seem to contribute to decreasing the time needed to finish the
experiment. However, the cause-effect relationship is not clear at
all. It might be the opposite: since experiments take longer to finish
and might in fact be abandoned with no one contributing for some time,
the probability of someone new joining them is higher. In fact,
with experiments taking a few seconds and due to the way the
experiments are announced, it is quite difficult that several
volunteers join in in such a short period of time, even more if we take
into account that volunteers are not {\em carried over} from previous
experiments. 
%
\begin{figure}[!htb]
\centering
\includegraphics[width=0.95\linewidth]{ips-per-minute-cache=64.png}
\caption{Simultaneous IPs every minute of the experiment with cache =
  64. \label{fig:otisdriftwood}}
\end{figure}
